Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-06 paper/ms.tex
reviewed abstract

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation matching the geometries of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
build such a model is to avoid the large uncertainties in the
estimation of \ly luminosities. Our main result is that the clustering
and number density information are insufficient to impose a tight
constraint on the {\bf occupation} fraction. On the other hand the
minimum mass and maximum mass can be tightly constrained to the range
$M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
10^{11.5}\hMsun$.  We also find that the consistent models have a narrow mass
range $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$
smaller than $1.0$ dex, with the vast majority in the range $\Delta
M<0.5$ dex. Already published constraints on the mass range and
occupation fraction are a sub-set of the models we report in this
\documentname. Our results present an inconclusive response as to
which is the occupation fraction for LAEs at $z=3.1$. A precise answer
requires observations on larger fields and robust physical models for
the connection between dark matter, star formation and the escape of
\ly radiation. That kind of modeling should also be able to provide a
plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.

>>>>

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density distribution and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation with the same geometry of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
1.0$. We avoid the large uncertainties in the estimation of \ly
luminosities with this approach. Our main result is that the
clustering and number density information are insufficient to impose a
tight constraint on the {\bf   occupation} fraction. On the other hand
the minimum mass and maximum mass can be constrained to the range $M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
10^{11.5}\hMsun$.  We also find that the consistent models have a narrow mass
range, $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$,
smaller than $1.0$ dex, with a vast majority in the range $\Delta
M<0.5$ dex. {\bf These mass ranges are a sub-set of already published
constraints, while the wide range of values for the escape fraction
  are a novel result}. There is an inconclusive response as to
which is the occupation fraction for LAEs at $z=3.1$. A precise answer
requires observations on larger fields and robust physical models for
the connection between dark matter, star formation and the escape of
\ly radiation. That kind of modeling should also be able to provide a
plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.
